Reinforcement Learning in Network Defence/Control (WIP)

### 2018-04-03 interim-talk/interim-talk.tex
Minor talk changes

\title{Reinforcement Learning in Network Defence/Control (WIP)}
\author{Kyle A. Simpson\\
	\tiny{\faGithub{} \href{https://github.com/felixmcfelix}{FelixMcFelix} \hspace{0.5em} \faGlobe{} \url{https://mcfelix.me}}}
\institute{University of Glasgow}
\date{\nth{10} April, 2018}

@@

\begin{frame}{An introduction}
	Yeah. \footcite{RL2E}

	Provide a rough explanation.
\end{frame}

>>>>

\title{Reinforcement Learning in Network Defence/Control (WIP)}
\author{Kyle A. Simpson\\
	\small{\faGithub{} \href{https://github.com/felixmcfelix}{FelixMcFelix} \hspace{0.5em} \faGlobe{} \url{https://mcfelix.me}}}
\institute{University of Glasgow}
\date{\nth{10} April, 2018}

@@

\begin{frame}{Introducing: Reinforcement Learning}
	\begin{itemize}
		\item Goal: train an agent to make optimal decisions based on observed state.
		\begin{itemize}
			\item Formally, maximise the \alert{expected discounted reward}\footcite{RL2E}.
		\end{itemize}

		\item Underlying theory: systems as (discrete-time) \alert{Markov Decision Processes}---states, actions, rewards and transition probabilities.
		\begin{itemize}
			\item I.e., choosing action $a_t$ from a policy in state $s_t$, $a_t \sim \pi(s_t)$, induces the next state $s_{t+1}$ and an associated reward $r_{t+1}$ stochastically.
			\item Generalises to \alert{value} $Q(s,a)$---how much reward can we \emph{eventually} expect from choosing each action currently available?
		\end{itemize}
	\end{itemize}
\end{frame}
